\section{Define the objectives and success metrics}\label{sec:define-the-objectives-and-success-metrics}

Use case: A person (any age, with/without symptoms) goes to the doctor and the doctor uses the model to make an evaluation.

\subsection{Objectives}\label{subsec:objectives}
Main objective: Enhance the quality of Catalonia’s public healthcare by implementing a predictive model that identifies chronic diseases before diagnosis. \\

Specific objectives:

\begin{itemize}
    \item Pre objective: Elaborate functional requirements documents in a meeting with the medical team. (Deliverable: Documentación)
    \item Develop Solution Model with detailed specifications.
    \item Achieve high quality dataset.
    \item Develop a model, to predict potential chronic diseases cases, with ease of explanation for doctors.
    \item Ethical document.
    \item Deliver an easy-to-use interface with a form and an easy to interpret result
    \item Source Code.
    \item Report of the performance of the predictive model on the Catalonia’s public healthcare
    \item Responsibilities and Licenses.

\end{itemize}

\subsection{Success Metrics}\label{subsec:success-metrics}
Main success metrics: Enhancement of the quality of Catalonia’s public healthcare by the usage of a predictive model that identifies chronic diseases before diagnosis. \\

Specific success metrics:

\begin{itemize}
    \item Functional requirements approved by consensus of the stakeholders.
    \item Solution Model Document approved by stakeholders.
    \item Quality of all features should be assured in accordance with the agreements in the solution model.
    \item Only models with at least 85\% recall are acceptable.
    \item Ethical document should be approved by consensus of the stakeholders. \\
    And approved in detailed by the Ethical Committee.
    \item Frontal: Achieve a System Usability Scale (SUS) score of 80+ in usability testing with doctors.
    \item Report of performance follows milestones and methodology of the project. \\
    All stakeholders are notified when the report is updated by a milestone.
    \item Licenses terms are approved by stakeholders and legal party.
\end{itemize}

\subsection*{Challenge}
\begin{warning}
    \textbf{Challenge}: It becomes increasingly more complicated to engage one of the stakeholders.
    \textbf{Solutions}:
    \begin{itemize}
        \item Have a more private conversation with the stakeholder who is not paying attention to us and ask about the reasons why they are not listening. Based on their response, adjust our communication strategy accordingly.
        \item Try to schedule meetings beforehand to ensure their availability, set clear expectations for the discussion and explain their importance for the project.
        \item Reach out to the stakeholder's supervisor and inform them that the stakeholder is not responding to us, only if we receive no answer from the stakeholder.
    \end{itemize}
\end{warning}


